\recipient{SpaceX Recruitment Team}{Rocket Road\\Hawthorne, California}
\date{September 17, 2015}
\opening{Dear Doug Knox,}
\closing{Sincerely,}
\enclosure[Attached]{curriculum vit\ae{}}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
\makelettertitle

It has come to my attention that your company is currently seeking Python developers for potential employment or internship; I am writing to submit my resume and apply for any openings that may so exist. 

I am currently completing a Bachelor's Degree in Computer Science at UCLA with expected graduation in Winter 2015, and have been concurrently employed as the Digital Content Administrator in the University's Hall of Fame; a museum which showcases over 100 years of athletic history and is open to the general public 7 days-a-week. In my tenure here, I have developed the technical plan and software for several new installations and supported many more in a wide variety of languages; these include Pauley Pavilion Wooden Way, as well as the Social Media Walls in the J.D. Morgan \& James West Alumni Centers.

Working as the lead technical administrator in an nontechnical field provided many unique opportunities: the opportunity to be solely responsible for the technical design and completion of mid-sized software projects; to work with mid-sized, real-world databases in a production environment; and design software for use by nontechnical users. This allowed me to gain valuable experience towards the whole of the software development process at an early point in my carrer, as well as given me an unusual amount of experience in automation scripting and tool design; tools and automation are essential when supporting and monitoring systems so heavily seen with such a small team.

It is my belief that these acquired skills make me an excellent fit for a support, scripting, or software development position at SpaceX. The chance to apply my automation and administration to the needs of a technical firm is something I'm both ready for and is necessary for my growth as a developer -- and the thought of in any way helping put things in space makes me giddy!

I would be happy to meet for an interview to further discuss the position and present my resume in person; I am reachable via the above email address or phone number.

\makeletterclosing